Dynamic strategies for yaw and induction control of wind farms based on large-eddy simulation and optimization

### 2018-01-02 MuntersMeyers_DynamicStrategiesControl_revision_WM01.tex
R2C10

\begin{table}
	\caption{Setup parameters for optimal dynamic induction and yaw control cases \label{tab:case_definition}}
	\centering
	\begin{tabular}{llccc}
		\toprule
		\multicolumn{5}{l}{\textbf{Simulation parameters}}\\
		\midrule
		Domain size  			& \multicolumn{4}{l}{$L_x \times L_y \times L_z = 4.8 \times 2.4 \times 1$ km$^3$}  \\ 
		Turbine dimensions  		& \multicolumn{4}{l}{$D = 0.1L_z = 100$ m}\\ 
		Turbine spacing  		& \multicolumn{4}{l}{$S_x = 6D, \quad S_y = 6D$}\\
		Windfarm layout 		& \multicolumn{4}{l}{$N_t = 16 $ turbines = 4 rows $\times$ 4 columns} \\ 
		Grid size 			& \multicolumn{4}{l}{$N_x \times N_y \times N_z = 256 \times 128 \times 128$}\\
		Cell size 			& \multicolumn{4}{l}{$\Delta_x \times \Delta_y \times \Delta_z = 18.75 \times 18.75 \times 7.8$ m$^3$}\\
		Time step 			& \multicolumn{4}{l}{$\Delta t = 0.75$ s}\\		
		& & & & \\	
		\multicolumn{5}{l}{\textit{Uniform inflow}}\\
		Hub height & \multicolumn{4}{l}{$z_h/L_z$ = 0.5}\\
		Inflow velocity & \multicolumn{4}{l}{$U_\infty$ = 8 m s$^{-1}$}\\
		& & & & \\			
		\multicolumn{5}{l}{\textit{Turbulent inflow}}\\
		Hub height & \multicolumn{4}{l}{$z_h/L_z$ = 0.1}\\		
		Precursor pressure gradient  	& \multicolumn{4}{l}{$ \partial_x p_\infty = 2.5 \times 10^{-4}$ m s$^{-2}$}  \\ 
		Surface roughness  &  \multicolumn{4}{l}{$z_0 = 10^{-4}H = 0.1$ m}\\ 		
		& & & & \\	
		\toprule
		\multicolumn{5}{l}{\textbf{Optimization parameters}}\\
		\midrule
		Optimization method		& \multicolumn{4}{l}{L--BFGS--B} \\
		Hessian correction pairs	& \multicolumn{4}{l}{$m = 5$} \\
		BFGS iterations 		& \multicolumn{4}{l}{$N_{it} = 80$ ($\approx 160$ PDE)} \\
		Optimization time window	& \multicolumn{4}{l}{$T = 300$ s}\\
		Flow advancement time window 	& \multicolumn{4}{l}{$T_A = 150$ s}\\
		Total operation time         	& \multicolumn{4}{l}{$T_{tot} = 900$ s (6 windows)}\\
		& & & & \\	
		\toprule
		\textbf{Cases} & \  & $C_{T,\text{min}}'$ & $C_{T,\text{max}}'$ & $\omega_{\text{max}}$ [$^\circ/s$] \\ 
		\toprule
		Reference & (R)    &  2 & 2 & 0   \\ 
		Yaw control & (Y)   &  2 & 2 & \textbf{0.3} \\ 
		Fast yaw control & (Y5)   &  2 & 2 &\textbf{5}   \\ 
		Underinduction control & (I2)    &  \textbf{0} & 2 & 0\\
		Overinduction control & (I3)    &  \textbf{0} & \textbf{3} & 0\\ 
		Underinduction + yaw control & (I2Y)   &  \textbf{0} & 2 & \textbf{0.3} \\ 
		Overinduction + yaw control & (I3Y)   &  \textbf{0} & \textbf{3} & \textbf{0.3} \\ 
		\bottomrule
	\end{tabular} 
\end{table}

>>>>

\begin{table}
	\caption{Setup parameters for optimal dynamic induction and yaw control cases \label{tab:case_definition}}
	\centering
	\begin{tabular}{llccc}
		\toprule
		\multicolumn{5}{l}{\textbf{Simulation parameters}}\\
		\midrule
		Domain size  			& \multicolumn{4}{l}{$L_x \times L_y \times L_z = 4.8 \times 2.4 \times 1$ km$^3$}  \\ 
		Turbine dimensions  		& \multicolumn{4}{l}{$D = 0.1L_z = 100$ m}\\ 
		Turbine spacing  		& \multicolumn{4}{l}{$S_x = 6D, \quad S_y = 6D$}\\
		Windfarm layout 		& \multicolumn{4}{l}{$N_t = 16 $ turbines = 4 rows $\times$ 4 columns} \\ 
		Grid size 			& \multicolumn{4}{l}{$N_x \times N_y \times N_z = 256 \times 128 \times 128$}\\
		Cell size 			& \multicolumn{4}{l}{$\Delta_x \times \Delta_y \times \Delta_z = 18.75 \times 18.75 \times 7.8$ m$^3$}\\
		Time step 			& \multicolumn{4}{l}{$\Delta t = 0.75$ s}\\		
		& & & & \\	
		\multicolumn{5}{l}{\textit{Uniform inflow}}\\
		Hub height & \multicolumn{4}{l}{$z_h/L_z$ = 0.5}\\
		Inflow velocity & \multicolumn{4}{l}{$U_\infty$ = 8 m s$^{-1}$}\\
		& & & & \\			
		\multicolumn{5}{l}{\textit{Turbulent inflow}}\\
		Hub height & \multicolumn{4}{l}{$z_h/L_z$ = 0.1}\\		
		Precursor pressure gradient  	& \multicolumn{4}{l}{$ \partial_x p_\infty \revision{/\rho} = 2.5 \times 10^{-4}$ m s$^{-2}$}  \\ 
		Surface roughness  &  \multicolumn{4}{l}{$z_0 = 10^{-4}H = 0.1$ m}\\ 		
		& & & & \\	
		\toprule
		\multicolumn{5}{l}{\textbf{Optimization parameters}}\\
		\midrule
		Optimization method		& \multicolumn{4}{l}{L--BFGS--B} \\
		Hessian correction pairs	& \multicolumn{4}{l}{$m = 5$} \\
		BFGS iterations 		& \multicolumn{4}{l}{$N_{it} = 80$ ($\approx 160$ PDE)} \\
		Optimization time window	& \multicolumn{4}{l}{$T = 300$ s}\\
		Flow advancement time window 	& \multicolumn{4}{l}{$T_A = 150$ s}\\
		Total operation time         	& \multicolumn{4}{l}{$T_{tot} = 900$ s (6 windows)}\\
		& & & & \\	
		\toprule
		\textbf{Cases} & \  & $C_{T,\text{min}}'$ & $C_{T,\text{max}}'$ & $\omega_{\text{max}}$ [$^\circ/s$] \\ 
		\toprule
		Reference & (R)    &  2 & 2 & 0   \\ 
		Yaw control & (Y)   &  2 & 2 & \textbf{0.3} \\ 
		Fast yaw control & (Y5)   &  2 & 2 &\textbf{5}   \\ 
		Underinduction control & (I2)    &  \textbf{0} & 2 & 0\\
		Overinduction control & (I3)    &  \textbf{0} & \textbf{3} & 0\\ 
		Underinduction + yaw control & (I2Y)   &  \textbf{0} & 2 & \textbf{0.3} \\ 
		Overinduction + yaw control & (I3Y)   &  \textbf{0} & \textbf{3} & \textbf{0.3} \\ 
		\bottomrule
	\end{tabular} 
\end{table}
